---
title: Examples
author: "Ian Lyttle"
date: "2017-02-02"
output: html_document
---

## vembedr

```{r setup, include=FALSE}
library("vembedr")
```

Easiest way to use is to grab the URL from the browser:

```{r}
embed_url("https://www.youtube.com/watch?v=uV4UpCq2azs")
```

Note: the "daily" build of RStudio puts the iframes from YouTube and Vimeo into the viewer.


```{r}
embed_url("https://youtu.be/1-vcErOPofQ?t=28s")
```

Get the suggested R code to embed:

```{r}
suggest_embed("https://www.youtube.com/watch?v=uV4UpCq2azs")
```

```{r}
suggest_embed("https://youtu.be/1-vcErOPofQ?t=28s")
```

Works the same with vimeo and UseR! 2016 videos:

```{r}
embed_url("https://channel9.msdn.com/Events/useR-international-R-User-conference/useR2016/Introducing-Statistics-with-intRo")
```

## bsplus

```{r}
library("lubridate")
library("htmltools")
library("bsplus")
```

### Accordion sidebar

We create an accordion-sidebar framework, then append.

```{r}
bs_accordion_sidebar(id = "beatles") %>%
  bs_append(
    title_side = "John Lennon", 
    content_side = "Rhythm guitar, vocals",
    content_main = "Dear Prudence"
  ) %>%
  bs_append(
    title_side = "Paul McCartney", 
    content_side = "Bass guitar, vocals",
    content_main = "Blackbird"
  ) %>%
  bs_append(
    title_side = "George Harrison", 
    content_side = "Lead guitar, vocals",
    content_main = "While My Guitar Gently Weeps"
  ) %>%
  bs_append(
    title_side = "Ringo Starr", 
    content_side = "Drums, vocals",
    content_main = "Don't Pass Me By"
  ) 

use_bs_accordion_sidebar()
```

### Carousel

We create a carousel framework, then append.

```{r}
bs_carousel(id = "with_the_beatles") %>%
  bs_append(content = bs_carousel_image(src = "img/john.jpg")) %>%
  bs_append(content = bs_carousel_image(src = "img/paul.jpg")) %>%
  bs_append(content = bs_carousel_image(src = "img/george.jpg")) %>%
  bs_append(content = bs_carousel_image(src = "img/ringo.jpg"))
```

### Tooltips, popovers

We embed tooltips and popovers into tags. Note the use of `bs_set_data()` to set the `data-delay` attribute according to the [Bootstrap options for tooltips](http://getbootstrap.com/javascript/#tooltips-options)

```{r}
tags$button(class = "btn btn-default", "John Lennon") %>%
  bs_embed_tooltip(title = "Rhythm Guitar, vocals") 

use_bs_tooltip()
```

```{r}
tags$button(class = "btn btn-primary", "John Lennon") %>%
  bs_embed_popover(
    title = "More information",
    content = "Although he wrote \"I Am the Walrus\", 
               he later insisted that the Walrus was Paul."
  )

use_bs_popover()
```

### Modal window

We create a modal window - it has an `id`.

```{r}
library("shiny") # need this for includeMarkdown()

bs_modal(
  id = "modal", 
  title = "Here's a title", 
  body = includeMarkdown("modal.md")
)
```

We then *attach* the `id` of the modal window, to as many buttons as we like.

```{r}
tags$button(class = "btn btn-default", "Click for modal") %>%
  bs_attach_modal(id_modal = "modal")
```

```{r}
tags$button(class = "btn btn-default", "New button, same modal") %>%
  bs_attach_modal(id_modal = "modal")
```

### bs_set_data

```{r}
tags$button(class = "btn btn-default", "John Lennon") %>%
  bs_embed_tooltip(title = "Rhythm Guitar, vocals") %>%
  bs_set_data(delay = dseconds(1))
```

## srlze

This is still very experimental.

```{r}
# install_github("ijlyttle/srlze")
library("srlze")
```

```{r}
list_in_r <- list(
  logical = TRUE,
  delay = as.difftime(5, units = "secs"),
  items = c("alpha", "beta", "gamma")
)

list_in_text <- serialize_list(list_in_r)

list_in_text
```


```{r}
serialize_list(
  list_in_r,
  delim = "|",
  locale = locale(
    logical_format = list(true = "True", false = "False"),
    dtime_format = "minute"
  )
)
```